DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-05-27 manuscript/manuscript.Rmd
updating figure 1 some more

At the time of writing of this manuscript (`r format(Sys.time(), "%b %d, %Y")`), DateLife's chronogram database latest version consist of `r length(opentree_chronograms$trees)` chronograms published in `r length(unique(opentree_chronograms$studies))` different studies. It is curated from OpenTree's phylogenetic database, the Phylesystem, which constitutes an open source of expert and peer-reviewed phylogenetic knowledge with rich metadata [@mctavish2015phylesystem], which allows automatic and reproducible assembly of our chronogram database. Datelife's chronogram database is navigable as an R data object within the `datelife` R package.

>>>>

At the time of writing of this manuscript 
,
<!--(`r format(Sys.time(), "%b %d, %Y")`), -->
DateLife's chronogram database latest version consist of `r length(opentree_chronograms$trees)` chronograms published in `r length(unique(opentree_chronograms$studies))` different studies. It is curated from OpenTree's phylogenetic database, the Phylesystem, which constitutes an open source of expert and peer-reviewed phylogenetic knowledge with rich metadata [@mctavish2015phylesystem], which allows automatic and reproducible assembly of our chronogram database. Datelife's chronogram database is navigable as an R data object within the `datelife` R package.

### 2022-05-27 manuscript/manuscript.tex
updating figure 1 some more

At the time of writing of this manuscript (May 27, 2022), DateLife's chronogram database latest version consist of 253 chronograms published in 187 different studies. It is curated from OpenTree's phylogenetic database, the Phylesystem, which constitutes an open source of expert and peer-reviewed phylogenetic knowledge with rich metadata (McTavish et al., 2015), which allows automatic and reproducible assembly of our chronogram database. Datelife's chronogram database is navigable as an R data object within the \texttt{datelife} R package.

@@

\begin{figure}[!h]
\includegraphics{../figures/figure-fringillidae/median_and_calibration_ages_simple.png}
\caption{Fringillidae median summary chronogram genertaed with DateLife. It has 256 tips and 233 nodes.}
\label{fig:fringillidages}
\end{figure}
% \begin{center}
% \textsc{Figure \ref{fig:fringillidages}}
% \end{center}

>>>>

At the time of writing of this manuscript
,
DateLife's chronogram database latest version consist of 253 chronograms published in 187 different studies. It is curated from OpenTree's phylogenetic database, the Phylesystem, which constitutes an open source of expert and peer-reviewed phylogenetic knowledge with rich metadata (McTavish et al., 2015), which allows automatic and reproducible assembly of our chronogram database. Datelife's chronogram database is navigable as an R data object within the \texttt{datelife} R package.

@@

\begin{figure}[!h]
\includegraphics{../figures/figure-fringillidae/median_and_calibration_ages_simple.png}
\caption{Fringillidae median summary chronogram generated with DateLife. It has 256 tips and 233 nodes.}
\label{fig:fringillidages}
\end{figure}
% \begin{center}
% \textsc{Figure \ref{fig:fringillidages}}
% \end{center}
